### 2022-11-14 NSF2022/Description/backgroundv3.tex
...

In the absence of external flow, the
system~\eqref{eq:RBT}--\eqref{eqn:stressbalance} has the energy law
\begin{align}
\label{eq:energy_law}
  \frac{d}{dt}E
  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2 \,d\xx,\quad
    E = \gamma \int_{\Omega(t)}
  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
\end{align}
Here $E$ is the energy stored by the phase transitions between the
granule boundaries and the solvent and the energy law states that the
granules move to decrease energy, which is lost due to viscous
dissipation. The derivation of~\eqref{eq:energy_law} is interesting
because $E$ depends both on $\phi$ and $\Omega(t)$. It uses the Rayleigh
Transport Theorem to write the time derivative of $E$ as an energy
density flux through the boundary involving the phase stress $T_i$, and
a bulk term involving the Euler-Lagrange derivative of
$E$~\cite{Fu2018_SIAM}. The Euler-Lagrange derivative vanishes due
to~\eqref{eqn:phase} and the boundary flux transforms into viscous
dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations.
Furthermore, the integral of the phase stress vectors $T_i\nnu$ over
$\partial \Omega$ is zero. Figure~\ref{fig:coarsening} summarizes the
general evolution of $E$ from the self-assembly process to the
collective dynamics of the assembly under external forcing.

>>>>

In the absence of external flow, the
system~\eqref{eq:RBT}--\eqref{eqn:stressbalance} has the energy law
\begin{align}
\label{eq:energy_law}
  \frac{d}{dt}E
  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2 \,d\xx,\quad
    E = \gamma \int_{\Omega(t)}
  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
\end{align}
Here $E$ is the energy stored by solvent phase transitions to the
boundary. It states that energy is always lost as viscous
dissipation. The derivation of~\eqref{eq:energy_law} is interesting
because $E$ depends both on $\phi$ and $\Omega(t)$. It uses the Rayleigh
Transport Theorem to write the time derivative of $E$ as an energy
density flux through the boundary involving the phase stress $T_i$, and
a bulk term involving the Euler-Lagrange derivative of
$E$~\cite{Fu2018_SIAM}. The Euler-Lagrange derivative vanishes due
to~\eqref{eqn:phase} and the boundary flux transforms into viscous
dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations.
Furthermore, the integral of the phase stress vectors $T_i\nnu$ over
$\partial \Omega$ is zero. Figure~\ref{fig:coarsening} summarizes the
general evolution of $E$ from the self-assembly process to the
collective dynamics of the assembly under external forcing.
